From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-06 Pi+/paper/finite.tex
Fix diagrams

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\Huge] at (2, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ 1, s_1}};
      \node[] at (1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.5, 0)
      {braid={ s_1, 1}};
      \node[font=\Huge] at (3, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (4, 0)
      {braid={ 1, s_1}};
      \node[] at (5.2, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (5.5, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\Huge] at (2, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (3, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\Huge] at (1.75, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (1.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.5, 0)
      {braid={ 1, s_1 }};
      \node[font=\Huge] at (3, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (4, 0)
      {braid={ 1, s_1}};
      \node[] at (5.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (5.5, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\Huge] at (2.15, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (3, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}
